



# Lab 2 4 Chocolate 20180201 

## Lab 2
```{r}
library(tidyverse)
```

```{r}
choco <- read.csv("https://ds202-at-isu.github.io/labs/data/choco.csv")
```

1. What is the overall number of chocolate bars rated?

```{r}
nrow(choco)
```

2. How does the number of ratings depend on the year? Draw a bar chart of the number of reports. 


```{r}
ggplot(choco, aes(x = Review.Date, fill = Review.Date)) + geom_bar()
```

This is a right-skewed distribution, so we can conclude that the number of ratings are more concentrated in 2014 ~ 2016. 


## Individual question set

1. How are ratings distributed?

```{r}
ggplot(choco, aes(x = Rating, fill = Rating)) + geom_histogram(binwidth = 0.5)
```
Most of the ratings are concentrated in 3 or 4. 


2. Do ratings depend on the cocoa percentage of a chocolate bar?

```{r}
ggplot(data = choco, aes(x = Cocoa.Pct, y = Rating)) + geom_point()
```
There is no significant correlation between cocoa percentage and rating since the data appears to be randomly scattered. 


3. How do ratings compare across different company locations?

```{r}
choco3 <- dplyr::filter(choco, Company.Location %in% c("U.S.A.", "France", "Canada"))
ggplot(data = choco3, aes(x = Company.Location, y = Rating)) + geom_boxplot()
```

Boxplot of France shows two outliers and USA shows only one outlier.



# Workflow: Working on Github is sometimes confusing. We are still learning. 
